%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~%
%                                       DECLARATION	                                      %
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~%
%\pagenumbering{roman} \setcounter{page}{2}
\thispagestyle{empty}
\begin{center}
{\Large{\bf{DECLARATION}}}
\end{center}

\noindent

I, \textbf{Ashish Kujur (Roll No: MSC21304)}, hereby declare that, this report entitled \textbf{“\ttle”} submitted to Indian Institute of Science Education and Research Thiruvananthapuram towards the partial requirement of Master of Science in School of Mathematics,  contains a literature survey of the work done by several experts in this area.  This project was carried out by me under the supervision of \textbf{Dr. Md. Ramiz Reza}.  To the best of my knowledge this work has not formed the basis for the award of any degree or diploma, in this or any other institution or university. I further declare that most of the results included in this thesis are based on the books such as \cite{hoffman2007banach}, \cite{mashreghi2009representation}, \cite{koosis1998introduction} and \cite{axler2013harmonic} mentioned in the bibliographical references. No new results have been created in this thesis. I have not misrepresented or fabricated or falsified any idea/data/fact/source in my submission. I have sincerely tried to uphold academic ethics and honesty by adequately citing and referencing the original sources. 

\vspace{4cm} % Reduce if text overflowing to a new page

\noindent Thiruvananthapuram - 695 551 \hfill \textbf{Ashish Kujur}

\noindent \today \hfill

\clearpage
