%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~%
%	                                    ACKNOWLEDGEMENT                                   %
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~%
\begin{center}
{\large{\bf{ACKNOWLEDGEMENT}}}
\end{center}
\thispagestyle{empty}


\noindent
I thank everyone who helped me see this project through to completion. I would like to first express my profound gratitude and deep regard to Dr. Md Ramiz Reza, IISER Thiruvananthapuram and sincerely wish to acknowledge his vision, guidance, valuable feedback and constant support throughout the duration of this project. I am grateful to him for his utmost patience even when I asked trivial questions. Earnest discussions with him made me more interested in mathematical analysis.

I am thankful to Pouchungong Gangmei, Suman Mondal, Nirmal Rawat, Bharath Krishna S and Joel Sleeba for all the discussions that we had for my project and theirs. I would like to thank all my MSc and IPhD batchmates for keeping me mentally sane with their jokes. I thank my family members who loved me thick and thin and at my worst. I would also like to thank the Mathematics Stackexchange community for helping me out in my project and mathematics in general since 2017.

Finally, I would like to thank Indian Institute of Science Education and Research for the necessary resources to complete the project to the best of my ability.

% Use words like "hard work", "helping every step of the way", 
% "sincere gratitude", "deepest appreciation", "highly indebted", "considerate endorsement", "honest and cooperative response", etc.
% "constant support, utmost patience and trust with respect to this project"
% "intuitiveness and insight have been invaluable to the progression of this project, allowing it to mature into the project it is today."
% "valuable guidance kept the project afloat especially with [his/her/their] fresh take with every stage of development of this project."
%"show my deepest appreciation towards my close friends and family for their pivotal care and well wishes and for encouraging me every step of the way"
%"wish to extend my sincere and heartfelt obligation towards"


\vspace{4cm} % Reduce if text overflows to a new page

\noindent Thiruvananthapuram - 695 551 \hfill \textbf{Ashish Kujur}

\noindent \today \hfill

\clearpage
