\chapter{The space \texorpdfstring{$H^1$}{\text{H1}}}

\section{Brief Recap!}
\begin{theorem}
    Let $u : \overline{\D} \to \C$ be a harmonic function. Then we have that
    \begin{equation*}
	u\left( re^{i\theta} \right) = \frac{1}{2\pi} \int_{-\pi}^{\pi} u\left( e^{it} \right) P_{r} \left( e^{i\left( \theta-t \right)} \right)
    \end{equation*}
    \label{thm:Poisson-Integral-Formula}
\end{theorem}

\section{The Helson-Lowdenslager Approach}
Let $\calC \left( \overline {\D} \right)$ be the set of all continuous functions on $\overline{\D}$ and let $H\left( \D \right)$ be the set of all holomorphic functions on the open disc $\D$. We define $\calA =\calC \left( \overline{ \D } \right) \cap H \left( \D \right)$.

We show that $\calA$ is an uniformly closed algebra of $\calC \left( \overline{ \D } \right)$. Let $\left\{ f_{n} \right\}$ be a sequence in $\calA$ converging uniformly to $f\in \calC \left( \overline \D \right)$.

We recall Morera's Theorem for analytic functions at this point:
\begin{theorem}[Morera]
    A continuous, complex valued function $f : D \to \C$ that satisfies $\oint _{\gamma} f \left( z \right) dz = 0$ for any closed piecewise $C^{1}$ path $\gamma$ in $D$ must be holomorphic on $D$.
    \label{thm:morera-analytic}
\end{theorem}

We use this theorem to prove what we want to prove. Now, let $C$ be any closed curve in $\D$. Then for any $n\in \mathbb N$,
\begin{align*}
\oint_{C}f_{n}  \left( z \right) dz = 0
\end{align*}
So, 
\begin{align*}
    \oint_{C} f(z) dz = \oint_{C} \lim_{n\to \infty} f_{n} \left( z \right) dz = \lim_{n\to \infty} \oint_{C} f_{n} \left( z \right) dz =0
\end{align*}
Since $C$ was arbitrary, $f$ must be holomorphic. This shows that $\calA$ is uniformly closed. The fact that it is an algebra is easy to check $\checkmark$.

Now, note that since $\D$ is a compact metric space, we have that $\calC \left( \D \right)$ is a complete metric space with supremum metric. Since the supremum metric can also be induced by a norm, namely the supremum norm, we have that $\calC\left( \D \right)$ is a Banach space with the supremum  norm.

Thus, this is what we have proved so far:

\begin{theorem}
    The disc algebra $\calA =\calC \left( \overline{ \D } \right) \cap H \left( \D \right)$ is a Banach space under the $\sup$ norm
    \begin{align*}
	\norm{f}_{\infty} = \sup_{\abs{z}\le 1} \abs{f\left( z \right)}
    \end{align*}
    \label{thm:disc-algebra-is-B-space}
\end{theorem}

We make a couple of observations at this point:
\begin{enumerate}
    \item Each $f\in \mathcal A$ is the Poisson integral of its boundary values:
\begin{align*}
    f\left( re^{i\theta} \right) = \frac{1}{2\pi} \int_{-\pi}^{\pi} f\left( e^{it} \right) P_{r} \left( e^{i \left( \theta -t \right)} \right) dt
\end{align*}
\item It follows from the Maximum Modulus Theorem that 
    \begin{align*}
	\norm{f}_{\infty} = \sup \abs{f\left( e^{it} \right)}
    \end{align*}
\end{enumerate}

\begin{theorem}[Correspondence of $\calA$ with a closed subspace of $\calC \left( \T \right)$]
    Consider the subspace
    \begin{align*}
	\tilde{\calA} = \left\{ f\in \calC \left( \T \right) \, : \, \int_{-\pi}^{\pi} f\left( e^{it} \right) e^{int}=0  \text{ for } n=1,2,\ldots \right\}
    \end{align*}
    of $\calC \left( \T \right)$. Then there is an isometric isomorphism of $\calA$ with $\tilde{\calA}$.
    \label{thm:correspondence-of-disc-algebra}
\end{theorem}
\begin{proof}
    First, we show that $\tilde{\calA}$ is a closed subspace of $\calC \left( \T \right)$. Let $\left\{ f_{n} \right\}$ be a sequence of functions in $\tilde{\calA}$ converging to $f\in \calC \left( \T \right)$. Consider the following:
    \begin{align*}
	\abs{\int_{-\pi}^{\pi} f\left( e^{it} \right) e^{ikt} dt} &= \abs{\int_{-\pi}^{\pi} f\left( e^{it} \right) e^{ikt} dt - \int_{-\pi}^{\pi} f_n\left( e^{it} \right) e^{ikt} dt}  \\
	&= \int_{-\pi}^{\pi} \abs{f \left( e^{it} \right) -f_{n} \left( e^{it} \right)} dt \\
	& \le 2\pi \norm{f_{n} - f}_{\infty} \to 0 \text{ as } n\to \infty
    \end{align*}
    This shows that $\tilde{\calA}$ is closed under $\calC \left( \T \right)$ with supremum norm.

    Now consider the linear map $T: \calA \to \tilde{\calA}$ given by
    \begin{align*}
	f \stackrel{T}{\longmapsto} f\mid_{\T}
    \end{align*}
    For the sake of convenience, we will write $f\mid_{\T}$ as $f_{\T}$.
    We first need to show this map is well defined! That is, we need to show that
    \begin{equation*}
	\int_{-\pi}^{\pi} f_{\T} \left( e^{it} \right) e^{ikt} dt = 0	
    \end{equation*}
    for all $k\in \N$ but this immediately follows from Cauchy's theorem.

    Note that injectivity is clear from Theorem \ref{thm:Poisson-Integral-Formula}. To show surjectivity, let $f\in \tilde{A}$. We need to show that there is a function $u \in \calA$ such that $u_{\T} = f$. Consider the function
    \begin{equation*}
	u\left( re^{i\theta} \right) =
	\begin{cases}
	    (P*f) (re^{i\theta}) & \text{ if } 0\le r <1 \\ 
	    f\left( e^{i\theta} \right) & \text{ if } r=1
	\end{cases}
    \end{equation*}
    This is the Dirichlet problem on the unit disc! So, $u$ is continuous on $\overline {\D}$. It remains to show that $u$ is analytic on $\D$. But note that for $r\in [0,1)$,
    \begin{align*}
    u\left( re^{i\theta} \right) &= \sum_{n=-\infty}^{\infty} r^{\abs{n}} \hat{f}\left( n \right) e^{int} \\
&= \sum_{n=0}^{\infty} r^{\abs{n}} \hat{f}\left( n \right) e^{int} 
    \end{align*}
    This completes the proof of the theorem!
\end{proof}

In view of the previous theorem, we will simply write $\tilde{\calA}$ as $\calA$.

\begin{definition}
    An analytic trignometric polynomial $p$ on the circle $\T$ is of the form
    \begin{equation*}
	p\left( e^{it} \right) = \sum_{k=0}^{n} a_{k} e^{ik\theta}
    \end{equation*}
    \label{def:trignometric-polynomial}
\end{definition}

\begin{proposition}
    The set of the trignometric polynomials is a dense subset of $\calA$.
    \label{prop:disc-algebra-separable}
\end{proposition}
\begin{proof}
    It is clear that any trignometric polynomial on the circle is a member of the disc algebra. Now, if $f: \T \to \C$ is in $\calA$, then its negative Fourier coefficients are zero! Since, the Cesaro sum of $f$ 
    \begin{equation*}
	s_{n} \left( x \right) = \sum_{k=-n}^{k=n} \hat{f} (n) e^{ikx} = \sum_{k=0}^{n} \hat{f} (n) e^{ikx}
    \end{equation*}
    converge to $f$ uniformly and is a sequence of trignometric polynomial, we are done!
\end{proof}

The following result is used in the proof of the next theorem, so, we prove it here:

\begin{theorem}
    The real parts of functions in $\calA$ are uniformly dense in $\calC \left( \T , \R \right)$. In other words, if $\mu$ is finite signed Borel measure on $\T$ such that $\int f \, d\mu =0$ for every $f\in \calA$ then $\mu$ is the zero measure.
    \label{thm:kinda-Fejer}
\end{theorem}
\begin{proof}
    We first show that any trignometric polynomial of the form
    \begin{equation}
	p\left( e^{it} \right) = \sum_{k=-n}^{n} c_{k} e^{ikt}
	\label{eqn:trig-poly-1}
    \end{equation}
    where $c_{-k} = \overline{c_{k}}$ for each $k\in \left\{ 1,\ldots , n \right\}$ is a real part of a function $f\in \calA$. Note that $p\left( e^{it} \right)$ in Equation \ref{eqn:trig-poly-1} is the real part of the function:
    \begin{equation*}
	f\left( e^{it} \right) = c_{0} + 2c_{1} e^{it} + 2c_{2} e^{2it} + \ldots + 2 c_{n} e^{int}
    \end{equation*}

    
    Now, we claim that every function $f \in C\left( \T , \R \right)$ is a uniform limit of a trignometric polynomial of the form \ref{eqn:trig-poly-1}. We will be done if we show that the negative Fourier coefficients of real valued function is the conjugate of the its positive counterpart, that is, for each $n\in \Z_{\ge 0}$, we have that $\hat{f}\left( -n \right) = \overline{\hat{f} \left( n \right)}$. To show this, take any $n\in \Z _{\ge 0}$ and then observe that
    \begin{align*}
	\hat{f} \left( -n \right) &= \int_{\T} f\left( e^{it} \right) e^{int} \frac{dt}{2\pi} \\
	&= \overline{\int_{\T} f\left( e^{it} \right) e^{-int} \frac{dt}{2\pi}} \\
&= \overline{\hat{f} \left( n \right)}
    \end{align*}

This shows that the Cesaro means of a real valued function is a trignometric polynomial of the form \ref{eqn:trig-poly-1} and since the Cesaro means converges to $f$ uniformly. Thus, the closure of the real parts of $\calA$ is indeed $\calC \left( \T , \R \right)$.

Now, let $\mu$ be a finite signed measure on $\T$ such that $\int f \, d\mu =0$ for every $f \in \calA$. We show that $\mu$ is the zero measure. Notice that if $f\in \calA$ then
\begin{equation*}
    0=\int_{\T} f \, d\mu = \int_{\T} \Re (f) \, d\mu + i\int_{\T} \Im (f) \, d\mu
\end{equation*}
Hence, it follows that 
\begin{equation*}
    \int_{\T} \Re (f) \, d\mu = 0
\end{equation*}
for every $f\in \calA$.
Now, if $g\in \calC \left( \T, \R \right)$ then by the first part of this theorem, there is a sequence $\left\{ f_{n} \right\} \in \calA$ such that $\Re \left( f_{n} \right) $ converges to $g$ uniformly. By the Dominated Convergence Theorem (which holds, thanks to Jordan Decomposition Theorem), we have that $\int_{\T} g \, d\mu = 0$. 

Now to prove that every $\mu = 0$, it suffices to show that $\hat{\mu} \left( n \right) = 0$ for every $n\in \Z$\footnote{See Page 41, Corollary 2.3 of Mashreghi.}. Now, notice that for any $n\in \Z$, we have
\begin{align*}
    \hat{\mu} (n) &= \int_{\T} e^{-int} d\mu \left( e^{it} \right) \\
    &=  \int_{\T} \left(\cos \left( nt \right) - i \sin \left( nt \right) \right) d\mu \left( e^{it} \right) \\
    &= \int_{\T} \cos \left( nt \right) d\mu \left( e^{it} \right) - i\int_{\T} \sin \left( nt \right) d\mu \left( e^{it} \right) \\
    &= 0
\end{align*}
This completes the proof!
\end{proof}

\begin{corollary}
    Let $\mu$ be a finite signed  measure on $\T$ such that $\int f d\mu = 0$ for every $f\in \calA$ which vanishes at the origin then $\mu$ is a constant multiple of Lebesgue measure.
    \label{cor:constant-multiple-of-Lebesgue}
\end{corollary}
\begin{proof}
    We first prove the following claim: If $f \in \calA$ then $\int_{\T} f d\mu = \frac{f\left( 0 \right)}{2\pi}$. Since the negative Fourier cofficients are zero and $f$ is continuous, we have that the Cesaro means converge uniformly to $f$, that is,
    \begin{align*}
	\sum_{k=0}^{\infty} \hat{f} \left( n \right) e^{int} \rightarrow f \text{ uniformly}
    \end{align*}
    Thus,
\begin{align*}
    \int_{T} f\left( e^{it} \right) \frac{dt}{2\pi} &= \frac{1}{2\pi} \int_{\T}  \left(  \sum_{k=0}^{\infty}\hat{f} \left( n \right) e^{int} \right) dt\\
    &= \frac{1}{2\pi} \sum_{k=0}^{\infty} \int_{\T} \left( \hat{f} \left( n \right) e^{int} dt \right) \\
    &= \frac{\hat{f}(0)}{2\pi} 
    \end{align*}

    Now, we proceed to the proof. We define a measure $d\nu = d\mu - \frac{1}{2\pi} \mu \left( \T \right) dt$. Now, we have that
    \begin{align*}
	\int_{\T} f\left( e^{it} \right) d\nu \left( e^{it} \right) &= \int_{\T}[f-f\left( 0 \right)] \left( e^{it} \right) d\mu \left( e^{it} \right) + f\left( 0 \right) \int_{\T} d\nu \left( e^{it} \right) \\
	&= 0
    \end{align*}
    Hence, we have that $d\mu = \frac{1}{2\pi} \mu \left( \T \right) dt$.
\end{proof}

We will be working entirely on the $\T$. So, $\calA$ and $H^{2}$ will be the spaces on the unit circle rather on the open unit disc. 

Now, consider $\calA$ as a subset of $L^{2} \left( \T , \scrB \left( \T \right) , \mu \right)$ where $\mu$ is any finite positive measure. Let $\calA _{0} = \left\{ f \in \calA : \int_{\T} f\left( e^{it} \right) \frac{dt}{2\pi} = \frac{\hat{f} (0)}{2\pi}=0 \right\}$. It is easily seen that $\calA _{0}$ is a subspace of $L^{2} \left( d\mu \right)$. Therefore, we have the closed subspace spanned by $\calA$ is $\llbracket \calA_{0} \rrbracket = \overline{ \operatorname{span} (\calA_{0}) } = \overline{\calA_{0}}$. By a theorem of Hilbert spaces, we have that there is some vector $F \in \llbracket \calA _{0} \rrbracket$ such that
\begin{equation*}
    \inf_{f\in \llbracket \calA _{0} \rrbracket} \int \abs{1-f^{2}} d\mu = \int \abs{1-F^{2}} d\mu
\end{equation*}

But since $d\left( 1, \llbracket \calA_{0}\rrbracket \right) = d \left( 1, \overline \calA_{0} \right) \stackrel{\footnote{this is true for any set in a metric space}}{=} d \left( 1, \calA_{0} \right)$, we have

\begin{equation*}
    \inf_{f\in \calA _{0}} \int \abs{1-f^{2}} d\mu = \int \abs{1-F^{2}} d\mu
\end{equation*}

Note that this $F$ is the orthogonal projection of $1$ into the closed subspace spanned by $\calA_{0}$.

\begin{theorem}
    Let $\mu$ be a finite positive Borel measure on $\T$ and suppose that the constant function $1$ is not in $\llbracket \calA_{0} \rrbracket$. Then let $f=P_{\llbracket \calA_{0} \rrbracket} \left( 1 \right)$. Then the following holds:
    \begin{enumerate}
	\item The measure $d\nu = \abs{1-F^{2}} d\mu$ is a nonzero constant multiple of the Lebesgue measure. In particular, Lebesgue measure is absolutely continuous with respect to $\mu$.
	\item The function $\left( 1-F \right)^{-1} \in H^{2}$.
	\item If $h= \left( \frac{d\mu}{d\theta} \right)$ then $\left( 1-F \right)h \in L^{2} = L^{2} \left( \frac{d\theta}{2\pi} \right)$.
    \end{enumerate}
    \label{thm:prelude-to-fm-riesz}
\end{theorem}

\begin{proof}
    \begin{enumerate}
	\item Let $S=\llbracket \calA _{0} \rrbracket$. We begin to prove part one of the theorem. Let $F= P_{S} \left( 1 \right)$. Then we have by the uniqueness of the decomposition that
    \begin{equation*}
	1=\underbrace{F}_{P_S (1)} + \underbrace{1-F}_{P_{S^{\perp} (1)}}
    \end{equation*}

    Thus, we have that $\left( 1-F \right)$ is orthogonal to every element in $S$ and hence, in particular, any element in $\calA _{0}$ (because $\calA_{0} \subset S \leadsto S^{\perp} \subset \calA_{0} ^{\perp}$). We claim that $1-F$ is orthogonal to $\left( 1-F \right) f $ for every $f\in \calA _{0}$.  But before, we do this, we need to show that $(1-F)f \in L^{2} (d\mu)$. Observe that\begin{align*}
	\int_{\T} \abs{(1-F)f^{2}} d\mu \le \norm{f}_{\infty}^{2} \norm{1-F}_{2}^{2} < \infty
    \end{align*}

    To prove this, note that we showed that $S=\overline{\calA_{0}}$ in the paragraph before the statement of this theoremand since $F \in S$, there is a sequence $\left\{ f_{n} \right\} \in \calA _{0}$ converging to $F$. Hence, we have that $\left\{ f\left( 1-f_{n} \right) \right\}$ is a sequence in $\calA _{0}$\footnote{$\calA_{0}$ is an algebra!} converges to $f\left( 1-F \right)$ in the $L^{2}$-norm. Hence, we have that

    \begin{align*}
	\ip{f(1-F), (1-F)} &= \ip{\lim_{n\to \infty} f\left( 1-f_{n} \right), \left( 1-F \right)} \\
	&= \lim_{n\to \infty} \ip{f\left( 1-f_{n} \right), \left( 1-F \right)} &\text{continuity of the inner product} \\
	&= 0  & \text{$1-F$ is orthogonal to $\calA_{0}$}
    \end{align*}
     
    Now, let $d\nu = \abs{1-F}^{2} d\mu$. We have shown that for any $f\in \calA_{0}$, 
    \begin{align*}
	\int_{\T} f d\nu &= \int_{\T} f \abs{1-F}^{2} d\mu = \ip{f(1-F), (1-F)} = 0
    \end{align*}
    Hence, by Corollary \ref{cor:constant-multiple-of-Lebesgue}, we have that $d\mu = k\, d\lambda$ for some $k \ge 0$.

    Now, we claim that this $k\ne 0$. If $k=0$ then we would have that 
    \begin{equation*}
	\int_{\T} d\nu = 0 \leadsto \int_{\T} \abs{1-F}^{2} d\mu = 0
    \end{equation*}
    Hence, we have that $F=1$ $\mu$-almost everywhere\footnote{See Corollary 2.3.12 of Cohn's Measure Theory.}. But then we have that $1\in S$ which contradicts our assumption. Hence $k \ne 0$.
\item Observe that part 1 of the theorem tells us that 
    \begin{equation*}
	\abs{1-F}^{2} d\mu = k\, d\lambda \text{ where } k \ne 0
    \end{equation*}
    Then we have that by Lebesgue Decomposition Theorem
    \begin{align*}
	d\mu = h d\lambda + d\mu_{s}
    \end{align*}
    for some positive $\calL^{1}$-function $h$ and some singular measure $\mu_{s}$.
    Hence, we have that
    \begin{align}
	\abs{1-F}^{2} d\mu &= \abs{1-F}^{2} \left( h d\lambda + d\mu_{s} \right) \\
	&= \underbrace{\abs{1-F}^{2} h d\lambda}_{(1)} + \underbrace{\abs{1-F}^{2} d\mu_{s}}_{(2)}
	\label{eqn:decomposed-measure}
    \end{align}
    By the uniqueness of the Lebesgue Decomposition Theorem (one needs to verify that the measures obtained in (1) and (2) are absolutely continuous and singular), we have that
\begin{align*}
    \abs{1-F}^{2} h &= k \text{ $\lambda$-almost everywhere.} \\
    \leadsto \frac{1}{\abs{1-F}^{2}} &= \frac{h}{k} \text{ $\lambda$-almost everywhere.}
\end{align*}
This tells us that $(1-F)^{-1} \in L^{2} \left( d\lambda \right)$ where $\lambda$ is the Lebesgue measure on $\T$. Also, note that $F=1$ $d\mu_{s}$-almost everwhere. Hence, we have that 
\begin{equation}
    \abs{1-F}^{2} d\mu = \abs{1-F}^{2} h d\lambda = k d\lambda \leadsto d\mu = \abs{1-F}^{-2} k d\lambda
    \label{eqn:prelude-to-f-m}
    \end{equation}

    Now, we proceed to show that the negative Fourier coefficients of $\left( 1-F \right)^{-1}$ is 0 then we would have shown that $\left( 1-F \right)^{-1} \in H^{2}$. Consider the following for $f\in \calA_{0}$:
\begin{align*}
    k \int_{\T} \left( 1-F \right)^{-1} f d\lambda &= k \int_{\T} \left( 1-\overline F \right) f \abs{1-F}^{-2} d\lambda \\
    &= k \int_{\T} \left( 1-\overline F \right) f d\mu \\
    &= 0
\end{align*}
The last line follows from the fact that $1-F \perp f$ for any $f\in \calA_{0}$. Hence this holds for any $e^{in\theta}$ and hence we are done.

\item Note that the derivative of $\mu$ with respect to normalized Lebesgue meaures is $h$ as demonstrated in Equation \ref{eqn:decomposed-measure}. Now, Equation \ref{eqn:prelude-to-f-m} shows that 
    \begin{align*}
	\abs{1-F}h = k\abs{1-F}^{-1} \text{ $\lambda$-almost everywhere.}
    \end{align*}
    Since $\abs{ 1-F}^{-1} \in L^{2} \left( \lambda \right)$, so is $(1-F)h$.
    \end{enumerate}
\end{proof}




\begin{corollary}
    Let $\mu$ be a finite positive measure on $\T$ with absolutely continuous part $\mu_{a}$, then
    \begin{align*}
	\inf_{f\in \calA_{0}} \int_{\T} \abs{1-f}^{2} d\mu = \inf_{f\in \calA_{0}} \int_{\T} \abs{1-f}^{2}  d\mu_{a}
    \end{align*}
    where $\mu_{a}$ is the absolutely continuous part of $\mu$.
    In particular, for any singular measure $\mu$, the function $1$ is in the $L^{2} \left( d\mu \right)$ closure of $\calA_{0}$.
\end{corollary}
\begin{proof}
    Let $F$ be the orthogonal projection of $1$ into the closed subspace spanned by $\calA_{0}$. Then we have that 
    \begin{align*}
	\inf_{f\in \calA_{0}} \int_{\T} \abs{1-f}^{2} d\mu = \norm{1-F}^{2} = \int_{\T} \abs{1-F}^2 d\mu
    \end{align*}
    From Equation \ref{eqn:prelude-to-f-m}, we see that
    \begin{equation*}
	\abs{1-F}^{2} d\mu = \abs{1-F}^{2} h d\lambda = \abs{1-F}^{2} d\mu_{a}
    \end{equation*}
    where $h$ is the Radon Nikodym derivative of $\mu$.
    Integrating both sides, we have that
\begin{align*}
	\inf_{f\in \calA_{0}} \int_{\T} \abs{1-f}^{2} d\mu = \inf_{f\in \calA_{0}} \int_{\T} \abs{1-f}^{2}  d\mu_{a}
    \end{align*}
    which is what we wanted to prove.
    Now if $\mu$ is a singular measure then we have that the absolutely continuous part of $\mu$ is the zero measure and hence we have that
\begin{align*}
	\inf_{f\in \calA_{0}} \int_{\T} \abs{1-f}^{2} d\mu = \norm{1-F}^{2} = 0   
    \end{align*}

    From the fact that $\norm{1-F}=0$, we conclude that $1=F$ almost everywhere and hence $1$ is in the closed subspace spanned by $\calA_{0}$ which is in fact $\overline {\calA_{0}}$. This completes the proof of the Corollary.
\end{proof}

\begin{corollary}
    Let $\mu$ be a finite complex Borel measure on $\T$ which is orthogonal to $\calA_{0}$, that is, $\int_{\T} f d\mu =0$ for all $f\in \calA_{0}$. Then the absolutely continuous part and singular parts of $\mu$ are separately orthogonal to $\calA_{0}$. That is, if $\mu_{a}$ and $\mu_{s}$ are the absolutely continuous and the singular parts of the measure $\mu$ then we have that
    \begin{align*}
	\int_{\T} f d\mu_{a} = 0 \text{ and } \int_{\T} f d\mu_{s} = 0
    \end{align*}
    for every $f\in \calA_{0}$. 
\end{corollary}
\begin{proof}
   Let $\rho$ be any finite positive measure satisfying
   \begin{enumerate}
       \item $\mu \ll \rho$ and $\frac{d\mu}{d\rho}$ is bounded, and
       \item $\frac{d\rho}{d\theta} \ge \frac{1}{2\pi}$, that is, the Radon Nikodym derivative with respect to the normalised Lebesgue measure is bounded below by $1/2\pi$.
   \end{enumerate}

   Let $d\mu = \frac{1}{2\pi} h d\theta + d\mu_{s}$ be the Lebesgue decomposition of the measure $\mu$. We define a new measure on $\T$ by 
   \begin{equation*}
       d\rho =  \left( 1+ \abs{h} \right) \frac{d\theta}{2\pi} + d\abs{\mu_{s}}
   \end{equation*}
   where $\abs{\mu_{s}}$ is the variation measure of the complex measure $\mu_{s}$, the singular part of $\mu$.

   We show that $\rho$ is an finite positive measure satisfying properties as in items 1 and 2 above. First, we show that $\rho$ is a finite positive measure. But before that note that the variation measure of any complex measure is  a finite measure.\footnote{See Cohn's Measure Theory -- Proposition 4.1.7}. Now, consider the following:
   \begin{align*}
       \rho\left( \T \right) &= \int_{\T} d\rho \\
       &= \int_{\T} \left( 1+ \abs{h} \right) \frac{d\theta}{2\pi} + \int_{\T} d\abs{\mu_{s}}  & \text{by definition} \\
       &= 1 + \abs{\mu_{a}} \left( \T \right) + \abs{\mu_{s}} \left( \T \right) & \mu_{a} \text{ is the absolutely continuous part of } \mu \\
       &< \infty
   \end{align*}
   Now we proceed to show that item 1 holds for $\rho$. First, we prove that $\mu \ll \rho$. Let $A \in \scrB \left( \T \right)$ with $\rho \left( A \right) = 0$. Then we have that
   \begin{align*}
       \int_{A} \left( 1+ \abs{h} \right) \frac{d\theta}{2\pi} &=0 \text{ and} \\
       \int_{A} d\abs{\mu_{s}} &= 0
   \end{align*}
   From this, we have that
   \begin{align*}
       \abs{\mu_{a}} \left( A \right) &=  \int_{A} \abs{h} \frac{d\theta}{2\pi} \\
       &\le \int_{A} \left( 1+\abs{h}  \right)\frac{d\theta}{2\pi} \\
       &= 0
   \end{align*}
   Since $\abs{\mu (A)} \le \abs{\mu_{a}} (A)$, we have that $\mu_{a} \left( A \right) = 0$. Also, it follows by the definition of the variation measure that $\mu_s \left( A \right) = 0$. Hence, we have that $\mu $ is absolutely continuous with respect to $\rho$. Now, we need to show that $\frac{d\mu}{d\rho}$ is bounded. \textcolor{red}{Needs work!}
We proceed to show that item 2 holds. Observe that
\begin{align*}
    \frac{d\rho}{d\theta} = \left( 1+\abs{h} \right) \frac{1}{2\pi} \ge \frac{1}{2\pi}
\end{align*}
and hence we are done showing that $\rho$ is such a measure.

Now, let $f\in \calA_{0}$. Then we have that
\begin{align*}
    \int_{\T} \abs{1-f}^{2} d\rho &= \int_{\T} \abs{1-f}^{2} \frac{d\rho}{d\theta} d\theta + \int_{\T} \abs{1-f}^2 d\mu_{s} \\
    &\ge \int_{\T} \abs{1-f}^{2} \frac{d\rho}{d\theta} d\theta \\
    & \ge \int_{\T} \abs{1-f}^{2} \frac{d\theta}{2\pi} \\ 
    &= \norm{1-f}^{2} \\
    &= \norm{1}^{2} + \norm{f}^{2} & \ip{f,1} = 0  \text{ as } f\in \calA_{0} \\
&\ge 1 
\end{align*}

Now, let $F$ be the orthogonal projection of $1$ into the closed subspace spanned by $\calA_{0}$ of $L^{2} \left( d\rho \right)$. Thus, by definition, we have that 
\begin{equation*}
    \int_{\T} \abs{1-F}^{2} = \inf_{f\in \calA_0} \int_{\T} \abs{1-f}^{2} d\rho \ge 1
\end{equation*}
Hence, we have that $1$ is not in the closed subspace spanned by $\calA_{0}$ of $L^{2} (d\rho)$. Hence, we have by Theorem \ref{thm:prelude-to-fm-riesz} that $\left( 1-F \right)^{-1} \in H^{2}$ and that 
\begin{equation*}
    \left( 1-F \right) \left( 1+\abs{h} \right) \in L^{2} = L^{2} \left( \frac{d\theta}{2\pi} \right)
\end{equation*}
From this, we can conclude that $h \in L^{2}$ by the following fashion:
\begin{equation*}
    \abs{h} = \underbrace{\left( 1-F \right) \left( 1+ \abs{h} \right)}_{\in L^{2}} \underbrace{\left( \abs{1-F}^{-1} \right)}_{\in H^{2} \leadsto \in L^{2}} -1
\end{equation*}
Hence, we have that $(1-F)h \in L^{2}$.

Suppose $g\in \calA_{0}$. We claim that
\begin{align*}
    \int_{\T} \left( 1-F \right) g d\mu = 0
\end{align*}
\end{proof}

Since $F\in \overline \calA_{0}$, there is a sequence $f_{n} \in \calA_{0}$ such that $f_{n} \to F$ in $L^{2} (d\rho)$. Hence,
\begin{align*}
    (1-f_{n})g \to \left( 1-F \right)g
\end{align*}
in $L^{2} \left( d\rho \right)$.

Since $\frac{d\mu}{d\rho}$ is bounded, we have that 
\begin{equation*}
    \int_{\T} \left( 1-F \right) g d\mu = \int_{\T} \left( 1-F \right) g \frac{d\mu}{d\rho} d\rho = \lim_{n\to \infty} \int_{\T} \left( 1-f_{n} \right) \frac{d\mu}{d\rho} d\rho = 0 \text{.}
\end{equation*}

Now, $1-F = 0$ with respect to $d\abs{\mu_{s}}$ which implies that $1-F= 0$ with respect to $d\mu_{s}$.

Thus, we have that 
\begin{align*}
    \left( 1-F \right) d \mu = \frac{1}{2\pi} \left( 1-F \right)h d\theta
\end{align*}

Hence, we have for $g \in \calA_{0}$
\begin{align*}
    \int_{\T} \left( 1-F \right) gh d\theta &= \int_{\T} (1-F)g d\mu  \\
    &= 0
\end{align*}

Since $\overline{A} = H^{2}$. There is a sequence of functions ${g_{n}}$ in $\calA$ converging to $\left( 1-F \right)^{-1} \in L^{2} \left( \frac{d\theta}{2\pi} \right)$ in $L^{2}$-norm. Hence, we have for any $f\in \calA_{0}$,
\begin{equation*}
    \int_{\T} g_{n}f\left( 1-F \right)h d\theta = 0
\end{equation*}


Also, note that $\left( 1-F \right)h \in L^{2}$. From this, we can conclude that 
\begin{equation*}
    \int_{\T} fh d\theta = 0
\end{equation*}

\begin{theorem}[Frigyez and Marcel Riesz, 1916]
    Let $\mu$ be a complex Borel measure on the unit circle $\T$ such that
    \begin{equation*}
	\int_{\T} e^{in\theta} d\mu \left( e^{i\theta} \right) =0
    \end{equation*}
    for all $n\in\N$. Then $\mu$ is absolutely continuous with respect to the Lebesgue measure.
    \label{thm:f-and-m-riesz}
\end{theorem}
\begin{proof}
    Suppose that $\mu$ is orthogonal to $\calA_{0}$. Then from the previous corollary, we have that $\mu_{a}$ is orthogonal to $\calA_{0}$ and $\mu_{s}$ is orthogonal to $\calA_{0}$. Since $\abs{\mu_{s}}$ is singular (definition?), we can find a sequence of functions $\left\{ f_{n} \right\}$ converging to $1$ in $L^{2} \left( d\abs{\mu_{s}} \right)$. Since $\mu_{s}$ is orthogonal to $\calA_{0}$, we have that
    \begin{equation*}
	\int_{\T} d\mu_{s} = \lim_{n\to \infty} \int_{\T} f_{n} d\mu_{s} = 0
    \end{equation*}
    Thus, $\mu_{s}$ is orthogonal to $1$. The singular measure $e^{-i\theta} d\mu_{s}$ is now orthogonal to $\calA_{0}$; hence it is orthogonal to $1$, that is, 
    \begin{equation*}
    \int_{\T} e^{-i\theta} d\mu_{s} = 0
    \end{equation*}
    Similarly, $e^{-2i\theta} d\mu_{s}$ is orthogonal to $\calA_{0}$, and consequently, orthogonal to $1$. Repeating thei process, we conclude that
    \begin{equation*}
	\int_{\T} e^{in\theta} = 0
    \end{equation*}
    for $n\in \Z$.
    Hence $\mu_{s}$ must be the zero measure. Therefore our original measure $\mu$ is absolutely continuous. 
\end{proof}
\section{Szegö's Theorem}
\begin{theorem}[Szegö]
    Let $h \in L^{1} \left( \T \right)$ and suppose that $h \ge 0$ on $\T$ (that makes $h$ real valued!). Then the following holds:
    \begin{align*}
	\exp \left[ \frac{1}{2\pi} \int_{-\pi}^{\pi} \log h\left( e^{it} \right) dt \right] = \inf_{f\in \calA_{0}} \frac{1}{2\pi} \int_{-\pi}^{\pi} he^{\Re \left( f \right)}dt
    \end{align*}
    \label{thm:prelude-to-szego-kolmorogoff-krein}
\end{theorem}
\begin{proof}
    We first claim that $\log h$ is integrable iff $\int \log h d\theta = -\infty$. To see this, first we decompose 
    \begin{align*}
	\int \log h d\theta = \underbrace{\int \left( \log h \right)^{+} d\theta}_{(\romannumeral1)} - \underbrace{\int \left( \log h \right)^{-} d\theta}_{(\romannumeral2)}
    \end{align*}
First observe that $\log h \le h$ (this follows by definition of $\log$) and hence, we have that $\left( \log h \right)^{+} \le h^{+}=h$. Thus, we have that integral $\left( \romannumeral1 \right)$ is finite. Therefore, $\log h$ is not integrable iff $\int \log h d\theta =- \infty$. 

    Regardless of integrability of $\log h$, we have the following relation:
    \begin{equation}
	\exp \left[ \frac{1}{2\pi} \int_{\T} \log h\left( e^{it} \right) dt \right] \le \frac{1}{2\pi} \int_{\T} h\left( e^{it} \right) dt
	\label{eqn:almost-am-gm}
    \end{equation}

    One can prove the famililar arithmetic and geometric means inequality from the above inequality. Let $n\in \N$ be arbitrary and $a_{1}, \ldots, a_{n}$ be positive real numbers. Let $A_{1}, A_{2}, \ldots , A_{n}$ be the disjoint subsets of $\T$ which cover it. Therefore, we have that
    \begin{align*}
	\mu \left( A_{i} \right) = \frac{2\pi}{n} \text{ for all } i=1,2,\ldots,n\text.
    \end{align*}
    Observe the following:
    \begin{align*}
	\log\left( a_{1} \chi_{A_{1}} + \ldots + a_{n} \chi_{A_{n}} \right) &= \log \left( a_{1} \chi_{A_{1}} + \ldots + a_{n} \chi_{A_{n}} \right) \\
	&= \log \left( a_{1} \right) \chi_{A_{1}} + \ldots + \log \left( a_{n} \right) \chi_{A_{n}}
    \end{align*}
    Integrating both sides, we get
    \begin{align*}
	\frac{1}{2\pi} \int_{\T} \log\left( a_{1} \chi_{A_{1}} + \ldots + a_{n} \chi_{A_{n}} \right) dt &= \frac{1}{2\pi} \int_{\T}  \log \left( a_{1} \right) \chi_{A_{1}} + \ldots + \log \left( a_{n} \right) \chi_{A_{n}} dt \\
	&= \frac{1}{2\pi} \left( \log \left( a_{1} \right) \mu \left( A_{1} \right) + \ldots +  \log \left( a_{n} \right) \mu \left( A_{n} \right) \right) \\
	&=  \log \left( \sqrt[n]{a_{1}\ldots a_{n}} \right)
    \end{align*}
     
    It can be seen now that it follows immediately.

    Now, if $h\in L^{\T}$ and is nonnegative, $g$ is any real valued continuous function on $\T$ then we have that $he^{g}$ is an nonnegative $L^{1} \left( \T \right)$ because product of an $L^{1}$ function with a bounded funtion on a finite measure space retains it back and therefore, we can apply Equation \ref{eqn:almost-am-gm}. Futhermore, if we assume that $\int_{\T} g dt =0 $ then we have that 
    \begin{align*}
	\exp\left[ \frac{1}{2\pi} \int_{\T} \log \left( h\left( e^{it} \right) e^{g\left( e^{it} \right)}\right) dt \right] \le \frac{1}{2\pi} \int_{\T} h\left( e^{it} \right) e^{g\left( e^{it} \right)} dt \\
	\leadsto \exp\left[ \frac{1}{2\pi} \int_{\T} \log \left( h\left( e^{it} \right) \right) dt + \cancelto{0}{\int_{\T} g\left( e^{it} \right) dt} \right] \le \frac{1}{2\pi} \int_{\T} h\left( e^{it} \right) e^{g\left( e^{it} \right)} dt \\
\leadsto \exp\left[ \frac{1}{2\pi} \int_{\T} \log \left( h\left( e^{it} \right) \right) dt  \right] \le \frac{1}{2\pi} \int_{\T} h\left( e^{it} \right) e^{g\left( e^{it} \right)} dt \\
    \end{align*}

    Now, let $g=\Re f$ for some $f\in \calA_{0}$. Then we have that $g$ is continuous and real valued and hence the previous inequality holds, therefore, we have that 

    \begin{equation*}
	\exp\left[ \frac{1}{2\pi} \int_{\T} \log \left( h\left( e^{it} \right) \right) dt  \right] \le \frac{1}{2\pi} \int_{\T} h\left( e^{it} \right) e^{\Re \left( f\left( e^{it} \right) \right)} dt \text{.}
    \end{equation*}
    Since $f \in \calA_{0}$ is arbitrary, we have that 
    \begin{equation*}
	\exp\left[ \frac{1}{2\pi} \int_{\T} \log \left( h\left( e^{it} \right) \right) dt  \right] \le \inf_{f\in\calA_{0}} \frac{1}{2\pi} \int_{\T} h\left( e^{it} \right) e^{\Re \left( f\left( e^{it} \right) \right)} dt \text{.}
    \end{equation*}

    Now, we claim the set of functions $\Re f$ where $f\in \calA$ is dense subset of $L^{1}_{\R}\left( \T \right)$. This is easy to see. Let $f\in L^{1}_{\R} \left( \T \right)$. Then denseness of continuous functions in $L^{1} _{\R}\left( \T \right)$, we have that there is some function $g\in \calC _{\R} \left( \T \right)$ such that 
    \begin{align*}
	\norm{f-g}_{1} < \frac{\varepsilon}{2}
    \end{align*}
    Also, by Theorem \ref{thm:kinda-Fejer}, we have that there is some function $h\in \calA$ such that 
    \begin{align*}
	\norm{g-\Re h}_{\infty} < \frac{\varepsilon}{2}
    \end{align*}
    Therefore, we have that
    \begin{align*}
	\norm{f-\Re h}_{1} & \le \norm{f-g}_{1} + \norm{g-\Re h} & \text{Minkowski inequality} \\
	& \le \norm{f-g}_{1} + \norm{f-g}_{\infty} & \text{finite measure space} \\
	& \le \frac{\varepsilon}{2} + \frac{\varepsilon}{2} = \varepsilon\text{.}
    \end{align*}

    This shows the denseness.

    Now, we show that the $\left\{ f\in L^{1}_{\R} \left( \T \right) : \int_{\T} f d\theta = 0 \right\}$ is dense in set of all functions $f \in L^{1}_{\R} \left( \T \right)$ such that $\int f d\theta = 0$. This is immediate because closure distributes over intersections and $\left\{ f\in L^{1}_{\R} \left( \T \right) : \int_{\T} f d\theta = 0 \right\}$ is a closed subspace of $L^{1}_{\R} \left( \R \right)$.

\end{proof}

